Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-04-04 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
updated paper version

# author citation list in chicago format
authorcitation: |
  Frery, A.C.; Alpala, J.; Nascimento,A.D.C.
# firstnote to eighthnote
#firstnote: |
 # Current address: Updated affiliation
#secondnote: |
  #These authors contributed equally to this work.
correspondence: |
  alejandro.frery@vuw.ac.nz
# document options
journal: remotesensing
type: article
status: submit
# front matter
#simplesummary: |
  #A Simple summary goes here.
abstract: |
  This paper presents a statistical approach to identify the underlying roughness characteristics in synthetic aperture radar (SAR) intensity data. The physical modeling of this kind of data allows to use the Gamma distribution in the presence of fully-developed speckle, i.e., when there are infinitely many independent backscatterers per resolution cell. This situation is often called "homogeneous" or 
  "textureless" areas. The $\mathcal{G}_I^0$ distribution is also a widely accepted law for heterogeneous and extremely heterogeneous areas. We propose three test statistics for discriminating between homogeneous and non-homogeneous areas, i.e., between Gamma and GI0 distributed data, both with a known number of looks. The first test statistic utilizes a bootstrapped non-parametric estimator of the Shannon entropy, offering a robust evaluation in the face of uncertain distributional assumptions. The second test uses the classic coefficient of variation. The third test employs an alternative form of estimating the CV based on the ratio of the median absolute deviation to the median. We apply our test statistic to produce maps of $p$-values for the hypothesis of homogeneity. These maps identify different types of targets. We show that our proposal outperforms its competitors using simulated and SAR data.
# back matter
keywords: |
  SAR; heterogeneity; entropy;  coefficient of variation; hypothesis tests
acknowledgement: |
  This study was financed in part by the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior - Brasil (CAPES) - Finance Code 001.
authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.
funding: |
  Please add: "This research received no external funding" or "This research 
  was funded by NAME OF FUNDER grant number XXX."  and ``The APC was funded 
  by XXX''. Check carefully that the details given are accurate and use the 
  standard spelling of funding agency names at 
  \url{https://search.crossref.org/funding}, any errors may affect your future 
  funding.
institutionalreview: |
 Not applicable.
#informedconsent: |
  # Any research article describing a study involving humans should contain this 
  # statement. Please add ``Informed consent was obtained from all subjects 
  # involved in the study.'' OR ``Patient consent was waived due to REASON 
  # (please provide a detailed justification).'' OR ``Not applicable'' for 
  # studies not involving humans. You might also choose to exclude this statement 
  # if the study did not involve humans.

  # Written informed consent for publication must be obtained from participating 
  # patients who can be identified (including by the patients themselves). Please 
  # state ``Written informed consent has been obtained from the patient(s) to 
  # publish this paper'' if applicable.
dataavailability: |
  Not applicable.
conflictsofinterest: |
  The authors declare no conflict of interest.
supplementary: |
 This article is fully reproducible using RMarkdown. All code and data are accessible at
 \url{https://github.com/rjaneth/Janeth-Alpala} (accessed on 10 March 2024).
abbreviations:
  - short: MDPI
    long: Multidisciplinary Digital Publishing Institute
  - short: DOAJ
    long: Directory of open access journals
  - short: TLA
    long: Three letter acronym
  - short: LD 
    long: linear dichroism

header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   - \usepackage[T1]{fontenc}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{amsmath}

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
#knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
library(RColorBrewer)
library(ggsci)
library(ggpubr)
library(patchwork)
library(dplyr)
#options(kableExtra.latex.load_packages = FALSE)
#library(devtools)
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(latex2exp)
library(e1071)# kurtosis
library(viridis)
library(nortest)# AD

@@

Synthetic Aperture Radar (SAR) technology has become an important tool for environmental monitoring and disaster management, providing valuable imagery in different conditions, including day or night and diverse weather situations&nbsp;\cite{Mu2019}.
However, the effective utilization of SAR data depends on a thorough understanding of its statistical properties, especially the impact of speckle effects, which are inherent in SAR data due to the coherent nature of the imaging process.

In the presence of non-Gaussian speckle interference, SAR data requires a reliable statistical model for accurate processing. The $\mathcal{G}^0$ distribution, suitable for SAR data, includes the Gamma law as a specific case for fully developed speckle, providing flexibility with fewer parameters for analysis.

@@

The entropy is a fundamental concept in information theory with broad applications to pattern recognition, statistical physics, stochastic dynamics, and statistics. 
Shannon introduced it for a random variable in 1948&nbsp;\cite{Shannon1948} as a measure of information and uncertainty.  
In statistics, Shannon entropy is a crucial descriptive parameter, particularly for assessing data dispersion and conducting tests for normality, exponentiality, and uniformity&nbsp;\cite{Wieczorkowski1999}. 
Entropy estimation involves several practical difficulties, especially when the model is unknown; in these cases, non-parametric methods are used.
Among the non-parametric approaches, Subhash et al.&nbsp;\cite{Subhash2021} discussed the use of spacing methods.
This non-parametric strategy offers flexibility to address a wide range of models without imposing specific parametric restrictions.
In our study, entropy serves as the fundamental parameter, providing a robust assessment by means of a bootstrapped non-parametric estimator of Shannon entropy.

Simultaneously, we used the classic coefficient of variation (CV) and an alternative form based on the ratio between the median absolute deviation and the median.
The coefficient of variation, recognised as an efficient and robust index of textural information, measures the homogeneity of the image.

@@

The article is structured as follows: 
Section&nbsp;\ref{sec:Background} covers statistical modeling and entropy estimation for Intensity SAR data. Section&nbsp;\ref{sec:test} outlines hypothesis testing based on non-parametric entropy estimators and and coefficient of variation. 
In Section&nbsp;\ref{sec:results}, we present experimental results. 
Finally, in Section&nbsp;\ref{sec:conclusion} conclusions are exhibited.

@@

## Statistical modeling of Intensity SAR data

@@

Using&nbsp;\eqref{E:entropy2}, we can express the Shannon entropy of $\Gamma_{\text{SAR}}$in&nbsp;\eqref{E:gamma1} and $G_I^0$ in&nbsp;\eqref{E:gi02} based on&nbsp;\cite{Cassetti2022} and&nbsp;\cite{Ferreira2020}:
\begin{equation}
\label{E:E-gamma}
H_{\Gamma_{\text{SAR}}}(L, \mu) =   L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) + \ln \mu, 
\end{equation}
\begin{multline}
\label{E:E-GIO}
H_{G_I^0}(\mu, \alpha, L) =L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) +\ln \mu -\ln\Gamma(L-\alpha)\\
+ (L-\alpha) \psi^{(0)}(L-\alpha)-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha)-L,
\end{multline}
where $\psi^{(0)}(\cdot)$ is the digamma function. Fig.&nbsp;\ref{fig:Plot_GI0_to_gamma1}, shows the behaviour of the entropy of \(G_I^0\) when when \(\alpha \in \left\{-\infty, -20, -8, -3\right\}\), observing its convergence towards the entropy of \(\Gamma_{\text{SAR}}\) as \(\alpha\) takes large negative values.

@@

In Fig.&nbsp;\ref{fig:Plot_bias_mse_gi0} we depict comparisons of bias and mean squared error (MSE) between the original non-parametric entropy estimators and their respective bootstrap-enhanced versions. 
The use of the bootstrap technique exhibits more precision, reduced bias and MSE, and improved convergence.
The results of simulation are exhibited in Table&nbsp;\ref{tab:table2}.

@@

# Hypothesis testing based on non-parametric entropy {#sec:test}

General asymptotic results for functions of spacings are detailed in Ref.&nbsp;\cite{Khashimov1990}, while Van Es&nbsp;\cite{Bert1992} developed a correction for the case of Shannon entropy.
Following the work of these authors, the next result applies: 
<!-- \begin{lemma} -->
<!-- Suppose that $f(\cdot)$ is a bounded density bounded away from zero and satisfies a Lipschitz condition on its support. -->
<!-- Then, if $m,n\rightarrow \infty$ and $m=o(n^{1/2})$, one holds that: -->
<!-- \begin{equation*} -->
<!-- \sqrt{n}\,\Big(\label{Eq:bias_t} -->
<!-- \widetilde{H}_{i}+\int_{-\infty}^\infty f(z)\ln f(z) \mathrm{d}z\Big) -->
<!-- \xrightarrow[]{\mathcal{D}} -->
<!-- \mathcal{N}\big(0,\operatorname{Var}(\ln f(Z))\big), -->
<!-- \end{equation*} -->
<!-- where $o(\cdot)$ represents the little-o. -->
<!-- \end{lemma}  -->

@@

$$
 \begin{cases}\mathcal{H}_0: \widetilde{H}= H_{\Gamma_{\text{SAR}}}\\ 
  \mathcal{H}_1:\widetilde{H}\neq H_{\Gamma_{\text{SAR}}}.\end{cases}
$$
In other words, we verify the hypothesis that the data are fully-developed speckle with the following test statistic:
\begin{equation}
\label{Eq:test_e}
S(\bm{Z};L)= \widetilde{H}-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \widebar{\bm{Z}}\right].
\end{equation}
<!-- This test statistic assess the behavior of the data under the null hypothesis, through the empirical distribution.  -->
The values should be around zero under the null hypothesis and far otherwise. 
<!-- This suggests significant differences and implies the presence of heterogeneous clutter. -->

# Results {#sec:results}

## The Proposed Test
Fig.&nbsp;\ref{fig:Plot_density} depicts empirical test statistic densities for various sample sizes, and Table&nbsp;\ref{tab:table_stat_combined} summarizes key statistics, including mean, SD, variance (Var), skewness (SK), excess kurtosis (EK), and Anderson–Darling $p$-values for normality. 
<!-- ACF Only show L=2 and L=8 -->
Results with $p$-values larger than $0.05$  indicate no evidence against normality. 
Small variance and near-zero skewness and excess kurtosis suggest limited spread, symmetry, and light tails.  
Normal QQ-plots, confirm that there is no evidence to reject the normal distribution.

@@

```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.pos="hbt",  fig.cap="Empirical density  under null hypothesis.", fig.width=6, fig.height=5.0}

@@

combined_summary_stats <- rbind(
  transform(summary_stats_2),
  transform(summary_stats_5),
  transform(summary_stats_8)

@@

table_result_combined <- knitr::kable(
  combined_summary_stats,
  caption = "Descriptive analysis of $S(\\bm Z; L)$ with $L\\in\\left\\{3,5, 8\\right\\}$ and $\\mu=1$.",
  format = "latex",
  booktabs = TRUE,
  align = "lrrrrrrr",
  escape = FALSE,
  digits = 4,
  label = "table_stat_combined",
  centering = FALSE,
  table.envir = "table", position = "H") %>%
  #table.env = 'table*' # to span multiple columns
  collapse_rows(latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")

@@

```{r Table_size_and_power, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#cat("\\setlength{\\tabcolsep}{4pt}\n")

load("./Data/type_I_results1.Rdata")

type_I_error_rates <- tapply(results$P_Value, INDEX = list(results$L, results$Sample_Size, results$Alpha_Nominal), FUN = function(p_values) {
  sum(p_values) / length(p_values)  
})

type_I_error_results <- as.data.frame(as.table(type_I_error_rates))

colnames(type_I_error_results) <- c("L", "Sample_Size", "Alpha_Nominal", "Type_I_Error_Rate")

spread_results <- spread(type_I_error_results, key = Alpha_Nominal, value = Type_I_Error_Rate)

spread_results <- spread_results %>% 
  select(L, Sample_Size, `0.01`, `0.05`, `0.1`)

load("./Data/results_power1.Rdata")

summary_stats <- results_power %>%
  spread(key = alpha_nominal, value = power) %>%
  select(L, Sample_Size, `0.01`, `0.05`, `0.1`)

combined_results <- merge(spread_results, summary_stats, by = c("L", "Sample_Size"))
combined_results <- combined_results %>% 
  arrange(L, Sample_Size)

combined_results <- combined_results %>% 
  select(L, Sample_Size, `0.01.x`, `0.05.x`, `0.1.x`, `0.01.y`, `0.05.y`, `0.1.y`)

colnames(combined_results) <- c("$L$", "$n$", "$1\\%$", "$5\\%$", "$10\\%$", "$1\\%$", "$5\\%$", "$10\\%$")

# LaTeX notation 
combined_results[] <- lapply(combined_results, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)
    } else {
      formatted_numbers <- ifelse(x < 0, sprintf("$%.3f$", x), sprintf("$\\phantom{-}%.3f$", x))
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})

table_combined_result <- knitr::kable(
  combined_results,
  caption = "Size and Power of the proposed test.",
  format = "latex",
  booktabs = TRUE,
  align = "lcccccccc",
  escape = FALSE,
  digits = 3,
  label = "table_size_power",
  centering = FALSE,
  linesep = "",
  table.envir = "table", position = "H")%>%
  add_header_above(c(" ", " ", "Size" = 3,  "Power" = 3)) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")

print(table_combined_result)

>>>>

# author citation list in chicago format
authorcitation: |
  Frery, A.C.; Alpala, J.; Nascimento,A.D.C.
# firstnote to eighthnote
#firstnote: |
 # Current address: Updated affiliation
#secondnote: |
  #These authors contributed equally to this work.
correspondence: |
  alejandro.frery@vuw.ac.nz
# document options
journal: remotesensing
type: article
status: submit
# front matter
#simplesummary: |
  #A Simple summary goes here.
abstract: |
  This paper presents a statistical approach to identify the underlying roughness characteristics in synthetic aperture radar (SAR) intensity data. The physical modeling of this kind of data allows to use the Gamma distribution in the presence of fully-developed speckle, i.e., when there are infinitely many independent backscatterers per resolution cell. This situation is often called "homogeneous" or 
  "textureless" areas. The $\mathcal{G}_I^0$ distribution is also a widely accepted law for heterogeneous and extremely heterogeneous areas. We propose three test statistics for discriminating between homogeneous and non-homogeneous areas, i.e., between Gamma and GI0 distributed data, both with a known number of looks. The first test statistic utilizes a bootstrapped non-parametric estimator of the Shannon entropy, offering a robust evaluation in the face of uncertain distributional assumptions. The second test uses the classic coefficient of variation. The third test employs an alternative form of estimating the CV based on the ratio of the mean absolute deviation from the median to the median. We apply our test statistic to produce maps of $p$-values for the hypothesis of homogeneity. These maps identify different types of targets. We show that our proposal outperforms its competitors using simulated and SAR data.
# back matter
keywords: |
  SAR; heterogeneity; entropy;  coefficient of variation; hypothesis tests
acknowledgement: |
  This study was financed in part by the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior - Brasil (CAPES) - Finance Code 001.
authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.
funding: |
  Please add: "This research received no external funding" or "This research 
  was funded by NAME OF FUNDER grant number XXX."  and ``The APC was funded 
  by XXX''. Check carefully that the details given are accurate and use the 
  standard spelling of funding agency names at 
  \url{https://search.crossref.org/funding}, any errors may affect your future 
  funding.
institutionalreview: |
 Not applicable.
#informedconsent: |
  # Any research article describing a study involving humans should contain this 
  # statement. Please add ``Informed consent was obtained from all subjects 
  # involved in the study.'' OR ``Patient consent was waived due to REASON 
  # (please provide a detailed justification).'' OR ``Not applicable'' for 
  # studies not involving humans. You might also choose to exclude this statement 
  # if the study did not involve humans.

  # Written informed consent for publication must be obtained from participating 
  # patients who can be identified (including by the patients themselves). Please 
  # state ``Written informed consent has been obtained from the patient(s) to 
  # publish this paper'' if applicable.
dataavailability: |
  Not applicable.
conflictsofinterest: |
  The authors declare no conflict of interest.
supplementary: |
 This article is fully reproducible using RMarkdown. All code and data are accessible at
 \url{https://github.com/rjaneth/identifying-heterogeneity-in-sar-data-with-new-test-statistics} (accessed on 5 April 2024).
# abbreviations:
#   - short: MDPI
#     long: Multidisciplinary Digital Publishing Institute
#   - short: DOAJ
#     long: Directory of open access journals
#   - short: TLA
#     long: Three letter acronym
#   - short: LD 
#     long: linear dichroism

header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   - \usepackage[T1]{fontenc}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{amsmath}
   - \usepackage{multirow}
   - \usepackage{subcaption}
   - \captionsetup[sub]{labelfont=bf,textfont=bf}

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
#knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
library(RColorBrewer)
library(ggsci)
library(ggpubr)
library(patchwork)
library(dplyr)
#options(kableExtra.latex.load_packages = FALSE)
#library(devtools)
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(latex2exp)
library(e1071)# kurtosis
library(viridis)
library(nortest)# AD
library(MASS)#
library(fitdistrplus)# model selection AIC and BIC

@@

Synthetic Aperture Radar (SAR) technology has become an important tool for environmental monitoring and disaster management, providing valuable imagery in different conditions, including day or night and diverse weather situations&nbsp;\cite{Moreira2013,Mu2019}.
However, the effective utilization of SAR data depends on a thorough understanding of its statistical properties, especially the impact of speckle effects, which are inherent in SAR data due to the coherent nature of the imaging process&nbsp;\cite{Argenti2013}.

In the presence of non-Gaussian speckle interference, SAR data requires a reliable statistical model for accurate processing. The $\mathcal{G}^0$ distribution, suitable for SAR data, includes the Gamma law as a limit case for fully developed speckle&nbsp;\cite{Ferreira2020}, providing flexibility with fewer parameters for analysis.

@@

The entropy is a fundamental concept in information theory with broad applications to pattern recognition, statistical physics, stochastic dynamics, and statistics. 
Shannon introduced it for a random variable in 1948&nbsp;\cite{Shannon1948} as a measure of information and uncertainty.  
In statistics, Shannon entropy is a crucial descriptive parameter, particularly for assessing data dispersion and conducting tests for normality, exponentiality, and uniformity&nbsp;\cite{Wieczorkowski1999,Zamanzade2012}. 
Entropy estimation involves several practical difficulties, especially when the model is unknown; in these cases, non-parametric methods are used.

Spacing methods have been discussed as a non-parametric approach in&nbsp;\cite{AlizadehNoughabi2010,Subhash2021}. 
This strategy offers flexibility to address a wide range of models without imposing specific parametric restrictions.

In our study, entropy serves as the fundamental parameter, providing a robust assessment by means of a bootstrapped non-parametric estimator of Shannon entropy.

Simultaneously, we use the classic coefficient of variation (CV) and an alternative form based on the ratio between the median absolute deviation and the median. 
The CV is known as an efficient and robust index of textural information, measures the homogeneity of the image&nbsp;\cite{Lopes1990}.

The CV, introduced by Pearson&nbsp;\cite{Pearson1896} in 1896, is a relative measure of dispersion widely used in various areas of applied statistics including sampling, biostatistics, medical and biological research, climatology, and other fields \cite{hendricks1936sampling, Tian2005,SubrahmanyaNairy2003,Chankham2024}.
It facilitates the comparison of variability between different populations and is especially valuable for comparing variables with different units. 
This is because when the main purpose is to compare variations of several variables, the standard deviation cannot serve as an adequate measure of variation unless all variables are expressed in the same unit of measurement and have identical mean values. 
When these requirements are not hold for the variables under study, CV is the relative measure typically used in real applications. 
The variable with the highest CV value is the one with the highest relative dispersion around the mean&nbsp;\cite{Banik2011}.

@@

The article is structured as follows: 
Section&nbsp;\ref{sec:Background} covers statistical modeling and entropy estimation for Intensity SAR data. Section&nbsp;\ref{sec:test} outlines hypothesis testing based on non-parametric entropy estimators and and coefficient of variation. 
In Section&nbsp;\ref{sec:Results}, we present experimental results. 
Finally, in Section&nbsp;\ref{sec:conclusion} conclusions are exhibited.

@@

## Statistical Modeling of Intensity SAR data

@@

Using&nbsp;\eqref{E:entropy2}, we can express the Shannon entropy of $\Gamma_{\text{SAR}}$in&nbsp;\eqref{E:gamma1} and $G_I^0$ in&nbsp;\eqref{E:gi02} based on&nbsp;\cite{Cassetti2022} and&nbsp;\cite{Ferreira2020}:
\begin{equation}
\label{E:E-gamma}
H_{\Gamma_{\text{SAR}}}(L, \mu) =   L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) + \ln \mu, 
\end{equation}
\begin{multline}
\label{E:E-GIO}
H_{G_I^0}(\mu, \alpha, L) =L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) +\ln \mu -\ln\Gamma(L-\alpha)\\
+ (L-\alpha) \psi^{(0)}(L-\alpha)-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha)-L,
\end{multline}
where $\psi^{(0)}(\cdot)$ is the digamma function. Figure&nbsp;\ref{fig:Plot_GI0_to_gamma1}, shows the behaviour of the entropy of \(G_I^0\) when when \(\alpha \in \left\{-\infty, -20, -8, -3\right\}\), observing its convergence towards the entropy of \(\Gamma_{\text{SAR}}\) as \(\alpha\) takes large negative values.

@@

In Figure&nbsp;\ref{fig:Plot_bias_mse_gi0} we depict comparisons of bias and mean squared error (MSE) between the original non-parametric entropy estimators and their respective bootstrap-enhanced versions. 
The use of the bootstrap technique exhibits more precision, reduced bias and MSE, and improved convergence.
The results of simulation are exhibited in Table&nbsp;\ref{tab:table2}.

@@

## Coefficient of variation and a robust alternative

The population CV is defined as a ratio of the population standard deviation $(\sigma)$ to the population mean $(\mu)$:

\begin{align}
	\text{CV}=\frac{\sigma}{\mu}, \quad \mu \neq 0.
\end{align}

<!-- In practice, the population CV is unknown and needs to be estimated.  -->
<!-- The typical sample estimate of the population CV is given as: -->
<!-- \begin{align} -->
<!-- 	\text{CV}=\frac{S}{\bar{X}},  -->
<!-- \end{align} -->
<!-- where $S$ and $\bar{X}$ are the sample standard deviation and the sample mean, respectively. -->

We explore a robust alternative to the CV as discussed in \cite{Ospina2019}, involving the ratio of the mean absolute deviation from the median (MnAD) to the median, two well-known robust measures of scale and location, respectively. The MnAD is defined as $n^{-1}\sum_{i=1}^n|x_i-\widehat{Q}_2|$, where $\widehat{Q}_2$ represents an estimate of the population median, which can be approximated by the sample median.

# Hypothesis Testing  {#sec:test}

@@

$$
 \begin{cases}\mathcal{H}_0: \text{ The data comes from the } \Gamma_{\text{SAR}}\\ 
  \mathcal{H}_1:\text{ The data comes from the } G_I^0.\end{cases}
$$
In other words, we verify the hypothesis that the data are fully-developed speckle.
The proposed tests are described below.

## The Proposed Test Based on Non-parametric Entropy

The first test statistic assess the behavior of the data under the null hypothesis, through the empirical distribution.
\begin{equation}
\label{Eq:test_e}
S_H= \widetilde{H}-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \widebar{Z}\right].
\end{equation}
The values should be around zero under the null hypothesis and far otherwise. 
<!-- This suggests significant differences and implies the presence of heterogeneous clutter. -->

Figure&nbsp;\ref{fig:Plot_density} depicts empirical test statistic densities for various sample sizes, and Table&nbsp;\ref{tab:table_stat_combined} summarizes key statistics, including mean, SD, variance (Var), skewness (SK), excess kurtosis (EK), and Anderson–Darling $p$-values for normality. 
<!-- ACF Only show L=2 and L=8 -->
Results with $p$-values larger than $0.05$  indicate no evidence against normality. 
Small variance and near-zero skewness and excess kurtosis suggest limited spread, symmetry, and light tails.  
Normal QQ-plots, confirm that there is no evidence to reject the normal distribution.

@@

```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.pos="hbt",  fig.cap="Empirical density  under the null hypothesis.", fig.width=6, fig.height=5.0}

@@

load("./Data/results1_11.Rdata")
summary_stats_11 <- all_summary_stats[["11"]]

combined_summary_stats <- rbind(
  transform(summary_stats_2),
  transform(summary_stats_5),
  transform(summary_stats_8),
  transform(summary_stats_11)

@@

table_result_combined <- knitr::kable(
  combined_summary_stats,
  caption = "Descriptive analysis of $S_H$ with $L\\in\\left\\{3,5, 8,11\\right\\}$ and $\\mu=1$.",
  format = "latex",
  booktabs = TRUE,
  align = "lrrrrrrr",
  escape = FALSE,
  digits = 4,
  label = "table_stat_combined",
  centering = FALSE,
  table.envir = "table", position = "H") %>%
  #table.env = 'table*' # to span multiple columns
  collapse_rows(latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")

@@

## The Proposed Test Based on Coefficient of Variation and a Robust Alternative

In addition to the entropy-based test, we also propose a test statistic based on the classical CV. This test statistic is defined as follows:
\begin{align}
	T_{\text{CV}}=\frac{S}{\widebar{Z}},
\end{align}
where $S$ and $\widebar{Z}$ are the sample standard deviation and the sample mean, respectively.

Similarly, we use another test statistic based on the ratio of the MnAD to the median. This statistic is given by:
\begin{align}
	T_{\text{CV}_{\text{MnAD}}}=\frac{\text{MnAD}}{\text{Median}}.
\end{align}
These test statistics allow assessing the variability of the data.

The situations where the use of CV and $\text{CV}_{\text{MnAD}}$ may be appropriate, i.e. where the observations are positive, the log-normal (LN) and inverse Gaussian (IG) distribution are often more justified compared to Gamma and Weibull distributions \cite{Chaubey2017,takagi1997application}.

The inverse Gaussian distribution is shown to be well approximated by the log-normal distribution \cite{whitmore1978} which implies that the IG distribution also does not share the problem of non-existence of fixed width confidence interval with the Gaussian case.

The LN distribution in two parameters has the following density function.
\begin{align}
	f_Z(z;\mu, \sigma )=\frac{1}{\sigma z\sqrt{2\pi}}\exp\left\{-\frac{(\ln z- \mu)^2}{2\sigma^2}\right\}, \quad z>0, \sigma>0, -\infty < \mu < \infty,
\end{align}
here, $\mu$ is the log-scale parameter and $\sigma$ is the shape parameter.

## Model Selection Criterion

Akaike information criterion (AIC) and Bayesian information criterion (BIC) are used to select the best fitting distribution.

The AIC is a fine technique that deals with the trade-off between the goodness-of-fit of the model and the simplicity of the model in terms of the number of model parameters&nbsp;\cite{Burnham2004}. 
The model or distribution with the lowest value of AIC is chosen to be the best.
The BIC assesses goodness-of-fit of a distribution or model, but avoids overfitting by penalising an additional degree of freedom&nbsp;\cite{Dziak2019}. 
The model with the lowest BIC value is chosen as the best.

The AIC and BIC results in Tables&nbsp;\ref{tab:table_aic_gamma}-\ref{tab:table_aic_gio_MnADmedian} indicate that the CV and $\text{CV}_{\text{MnAD}}$ data from different synthetic sample sizes, extracted from the Gamma SAR and $G_I^0$ distributions, respectively, adhere to the characteristics of an LN distribution.
The AIC and BIC values of the IG distribution and the LN distribution are not significantly different because both distributions are based on the right-skewed characteristic.
In this situation, the model for the LN distribution was considered to be the best due to it providing the lowest AIC and BIC values.

Figures&nbsp;\ref{fig:Plot_cv}-\ref{fig:Plot_madmed_gi0_MnADmedian} present density plots, Q-Q plots, P-P plots, and Cumulative Distribution Function plots, which offer an additional measure of goodness-of-fit and confirm that the most suitable distribution to be considered is the LN distribution.

```{r Simulated_AIC_BIC_gamma, echo=FALSE, message=FALSE, warning=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")
R <- 15000
mu <- 1
L <- 5
#B <- 5
#alpha1 <- -3
sample.sizes <- c(25, 49, 81, 121)

results_AIC <- data.frame(Test = character(),
                          SampleSize = integer(),
                          Normal = numeric(),
                          Lognormal = numeric(),
                          Gamma = numeric(),
                          Weibull = numeric(),
                          InverseGaussian = numeric())

results_BIC <- data.frame(Test = character(),
                          SampleSize = integer(),
                          Normal = numeric(),
                          Lognormal = numeric(),
                          Gamma = numeric(),
                          Weibull = numeric(),
                          InverseGaussian = numeric())

for (s in sample.sizes) {
  TestStatistics <- numeric(0)

  for (r in 1:R) {
    z <- gamma_sar_sample(L, mu, s)
    #z <- gi0_sample(mu, alpha1, L, s)
    TestStat <- sd(z) / mean(z)
    TestStatistics <- c(TestStatistics, TestStat)
  }

  fit_weibull <- fitdistr(TestStatistics, "weibull")
  fit_lognormal <- fitdistr(TestStatistics, "lognormal")
  fit_gamma <- fitdistr(TestStatistics, "gamma")
  fit_normal <- fitdistr(TestStatistics, "normal")

  AIC_values <- c(AIC(fit_weibull), AIC(fit_lognormal), AIC(fit_gamma), AIC(fit_normal))
  BIC_values <- c(BIC(fit_weibull), BIC(fit_lognormal), BIC(fit_gamma), BIC(fit_normal))

  dinvgauss <- function(x, mu, lambda) {
    sqrt(lambda / (2 * pi * x^3)) * exp(-lambda * (x - mu)^2 / (2 * mu^2 * x))
  }

  negLL_invgauss <- function(params, data) {
    mu <- params[1]
    lambda <- params[2]
    CV <- data

    -sum(log(dinvgauss(CV, mu, lambda)))
  }

  fit_invGauss <- fitdist(data = TestStatistics, distr = "invgauss", method = "mle",
                          start = list(mu = mean(TestStatistics), lambda = var(TestStatistics)))

  log_likelihood <- logLik(fit_invGauss)
  num_params <- length(coef(fit_invGauss))
  n <- length(TestStatistics)
  AIC_manual <- -2 * log_likelihood + 2 * num_params
  BIC_manual <- -2 * log_likelihood + num_params * log(n)

  results_AIC <- rbind(results_AIC, data.frame(Test = "AIC",
                                               SampleSize = s,
                                               Normal = AIC_values[4],
                                               Lognormal = AIC_values[2],
                                               Gamma = AIC_values[3],
                                               Weibull = AIC_values[1],
                                               InverseGaussian = AIC_manual))

  results_BIC <- rbind(results_BIC, data.frame(Test = "BIC",
                                               SampleSize = s,
                                               Normal = BIC_values[4],
                                               Lognormal = BIC_values[2],
                                               Gamma = BIC_values[3],
                                               Weibull = BIC_values[1],
                                               InverseGaussian = BIC_manual))
}

save(results_AIC, results_BIC, file = "./Data/results_AIC_BIC_gamma.Rdata")

```{r Table_AIC_BIC_gamma, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

load("./Data/results_AIC_BIC_gamma.Rdata")

combined <- rbind(results_AIC, results_BIC)
rownames(combined) <- NULL

colnames(combined) <- c("\\textbf{Criterion}", "$\\bm{n}$", "\\textbf{Normal}", "\\textbf{Lognormal}", "\\textbf{Gamma}", "\\textbf{Weibull}", "\\textbf{Inverse Gaussian}")

#combined$`Inverse Gaussian` <- c("\\multirow{2}{*}{Inverse}", "Gaussian")

# LaTeX notation 
combined[] <- lapply(combined, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)
    } else {
      formatted_numbers <- ifelse(x < 0, sprintf("$%.2f$", x), sprintf("$\\phantom{-}%.2f$", x))
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})

table_result_combined <- knitr::kable(
  combined,
  caption = "AIC and BIC values for evaluating the best distribution with CV data from Gamma SAR.",
  format = "latex",
  booktabs = TRUE,
  align = "lccccccc",
  escape = FALSE,
  digits = 2,
  label = "table_aic_gamma",
  centering = FALSE,
  table.envir = "table", position = "H") %>%
  collapse_rows(latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")

print(table_result_combined)
```
